SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-23 Chapters/Chapter02.tex
recompiling..
SDM Typos.

Suddenly, you feel the danger.  You tighten your grip on the child's hand and step up your walking.  In these large cities, walking on a dark alley was never recommended, but somehow that's what you did, and now everthing you think of is to get out to safety.  You are afraid of something, but you cannot explain --- in rigorous detail, at least --- what exactly is causing your fear. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing precisely what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. The whole process happens so fast it feels like it only took a single unit of psychological time.

>>>>

Suddenly, you feel the danger.  You tighten your grip on the child's hand and step up your walking.  In these large cities, walking on a dark alley was never recommended, but somehow that's what you did, and now everything you think of is to get out to safety.  You are afraid of something, but you cannot explain --- in rigorous detail, at least --- what exactly is causing your fear. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing precisely what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. The whole process happens so fast it feels like it only took a single unit of psychological time.
